Paper Report

### 2017-11-18 Paper_report.tex
HMM Unsupervised for MT

\subsection{Probability approach}
Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM. In general, we try to calculate the probability by using two different neural networks.The significant point of NN is embedding context.

They use Generalized EM to estimate $\theta$, \eqref{Word Alignment Model Neural Network p(f,e)} becomes:

$p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)$ \\

$ = E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ] + H[q(a_1^J)] + KL(q(a_1^J) \| p_{\theta}(a_1^J|f_1^J,e_1^I) ) $ \\

Updating $\theta$ requires only maximizing $E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ]$. The gradient is: \\
\marginpar{Why?: See \citep{Tran16unsupervised}}

$ J(\theta) = \sum_{a_1^J} \quad q(a_1^J)\quad ln \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $

>>>>

\subsection{Probability approach}
\subsubsection{\cite{Tran16unsupervised}}
Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM. In general, we try to calculate the probability by using two different neural networks.The significant point of NN is embedding context.

\begin{enumerate}
\item They use Generalized EM to estimate $\theta$, \eqref{Word Alignment Model Neural Network p(f,e)} becomes:\\

$p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)$

$ = E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ] + H[q(a_1^J)] + KL(q(a_1^J) \| p_{\theta}(a_1^J|f_1^J,e_1^I) ) $

\item Updating $\theta$ requires only maximizing $E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ]$. \\ The gradient is: \\
\marginpar{Why?: See \citep{Tran16unsupervised}}

$ J(\theta) = \sum_{a_1^J} \quad q(a_1^J)\quad \bigtriangledown log \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $

\item In the step E, we model $q(a_1^J) = p_{\theta'}(a_1^J|f_1^J,e_1^I)$.
Therefore,\\

$ J(\theta) = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown log \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $

\item From \eqref{Och2003Systematic Alignment Model Equation}, we have \\
$p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1})$  with the assumptions about I, J.
Therefore, \\

$ J(\theta) = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown log \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $

$ = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown log \, [\prod_{j=1}^J p_{\theta}(f_j | e_{a_j}) * p_{\theta}(a_j | a_{j-1})  ] $

$ = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown [\sum_{j=1}^J log \, p_{\theta}(f_j | e_{a_j}) + log \, p_{\theta}(a_j | a_{j-1})  ] $

$ = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j,e_{a_j}) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j,e_{a_j}) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ] $

\item We choose $a$ is state, $f$ is observation. We remove $e$.
Therefore, \\

$ J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ] $

\paragraph{How to apply NN ?}
\begin{itemize}
\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities of all source-language vocabulary.
\item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
\item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
\end{itemize}
